Git Learning Notes

### 2015-03-29 ch-moox/moox.tex
Final

Researchers have been exploring a variety of methods to synthesize different \ce{MoO3} nanostructures. Only a brief introduction will be given here, since these efforts has been well documented in several review articles.\cite{He2003} Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor deposition approaches.\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009} Both methods have their own merits. Hydrothermal process usually needs lower temperature(\textless 300 \si{\degreeCelsius}), but the reaction often requires tens of hours, and the sample requires several post-growth processing steps; whereas vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) with a few hours reaction time. Both methods are scalable for industrial applications. However, the hydrothermal treatment seems to allow more  nanostructures control than does the vapor deposition method. Nanobelts,\cite{Li2002b} helical nanosheets, nanoflowers, nanorods,\cite{Li2006a} and nanoribbons\cite{Camacho-Bragado2006} were obtained by the former one while nanoflakes,\cite{Chen2009} nanobelts,\cite{Hu2009} and nanowires\citep{Zhou2003b,Chen2011b} dominated the product morphology for the latter one. The assistance of Au catalyst in vapor deposition only altered the orientation\cite{Yan2009} or served as preferred nucleation sites\cite{Cai2011} without producing new \ce{MoO3} structures. \citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method and demonstrated the photodegradation of methylene blue (MB) under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity, and temperature was studied. h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH-} were possible structure directing and stable agents. The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0$ eV. Hexagonal phase of \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$). It is worth noting that in spite of these numerous growth of \ce{MoO3}, reports on catalytic growth are still scarce.

@@

Silicon substrate was first cleaned according to the procedures stated in Sec.~\ref{ch2sub} on page~\pageref{ch2sub} and directly used in non-catalyst-assisted experiment. In catalyst-assisted growth, hydrophilic Si substrates were first drop-cast with \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) solution (54 $\mu$L 10 mM) and then air dried in a chemical fume hood before experiment. Other alkali ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass (Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping. Mica was cleaved right before growth without other treatment. 
\begin{table}[htb]
\centering
\caption{Physical constants of reactants }\label{tb:mothermo}
\begin{tabular}{lccr}
\toprule
Material & MP(\si{\degreeCelsius}) & BP(\si{\degreeCelsius}) & Reference\\
\midrule
\ce{NaOH}        & 318 & 1388 & \cite{crc1977}  \\
\ce{NaI}         & 651 & 1300 & \cite{crc1977}    \\
\ce{KI}          & 681 & 1330 & \cite{crc1977}   \\
\ce{Na2CO3}      & 851 & Not determined & \cite{crc1977}    \\
\ce{Na2MoO4}     & 687 & Not available & \cite{crc1977}   \\
\ce{MoO3}    & 795 & 1155 & \cite{crc1977}   \\
\ce{MoO2}    & 1100(decomp) & Not available & MSDS   \\
\bottomrule
\end{tabular}
\end{table}
In a typical catalytic synthesis (Fig.~\ref{fig:mooxgrowth}), about 2 g molybdenum powders were loaded into the uniform heating zone, and the sealed chamber was first pumped down to 10 mTorr. 
% cvd layout
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{CVD_and_temp_MoO3.jpg}
\caption[CVD growth setup of \ce{MoO3}]{CVD growth setup of \ce{MoO3}. The triangular labels $\blacktriangledown$ were measured points at ambient environment.}
\label{fig:mooxgrowth}
\end{figure}
Oxygen flow, varying between 0.1 sccm to 10 sccm, was then admitted from the upstream inlet. With 10 sccm UHP Ar as carrier gas, the overall pressure reached about 200 mTorr. The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 min and lasted for 15 to 120 min. At last, the heating power was turned off, and the chamber was allowed to naturally cool to room temperature. The substrate was placed in downstream location where the temperature was about 350 to 650 \si{\degreeCelsius} according to open air temperature profile. Non-catalytic growth shared the same procedure except the NaOH treatment on Si substrates.

@@

As shown in Fig.~\ref{fig:mooxch}, the crystal structure and phase of the as-synthesized specimen were examined by XRD and Raman. The XRD pattern (Fig.~\ref{fig:moxrd}) was readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628 \AA, \emph{b}=13.855 \AA, and \emph{c}=3.6964 \AA). The space group is $D_{2h}^{16}(Pbnm)$. This crystal structure is indeed a unique example among transition metal oxides, representing a transitional stage between tetrahedra and octahedral coordination.\cite{Itoh2001a} The strongest peak index was (110), suggesting the orientation of \ce{MoO3} was not parallel to the substrate, in consistent with the morphology displayed in Fig.~\ref{fig:mosem1}. In contrast, different dominating orientation was observed in the XRD pattern from catalytic growth (Sec.~\ref{sec:nasi}).
% xrd raman
% 081113 sample
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:moxrd}\includegraphics[width=0.45\textwidth]{xrd_moo3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:moram}\includegraphics[width=0.45\textwidth]{raman_moo3}}
\caption[Crystalline phase characterization of \ce{MoO3} on Si]{Crystalline phase characterization of \ce{MoO3} on Si: (a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532$ nm.}
\label{fig:mooxch}
\end{figure}
The Raman spectrum of the as-synthesized specimen also closely matched \ce{MoO3} features observed in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the \ce{MoO3} flakes, and several inspections on different positions were observed to ensure the reproductivity of spectra data. As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved. The 284 \si{cm^{-1}} peak represented the wagging mode for double bond \ce{O=Mo=O}. The 337 and 380  \si{cm^{-1}} peaks were assigned to \ce{O-Mo-O} bending and scissoring modes, respectively. The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represented \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode, and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively. The 667 \si{cm^{-1}} peak was assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral. The 819 \si{cm^{-1}} peak arose from doubly coordinated oxygen stretching mode between two octahedral. The 996 \si{cm^{-1}} peak was from unshared oxygen stretching mode.\cite{Siciliano2009} The Raman symmetry assignment is summarized in Table~\ref{tab:moram}.
% raman assign
\begin{table}[htb]
\centering
\caption[Experimental Raman peaks assignment of \ce{MoO3} on Si]{Experimental Raman peaks assignment of \ce{MoO3} on Si.\cite{Eda1992,Siciliano2009}}\label{tab:moram}
\begin{tabular}{llcll}
\toprule
this work(\si{cm^{-1}}) & Sym.  &    & Assignment &   \\
\midrule
117      & $B_{2g}$    &           & $T_c$  & RCM\textsuperscript{\emph{a}}  \\
129      & $B_{3g}$    &           & $T_c$  & RCM  \\
158      & $A_g/B_{1g}$&           & $T_b$  & RCM  \\
199      & $B_{2g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
218      & $A_g$       &           & $R_c$     & RCM  \\
247      & $B_{3g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
284      & $B_{2g}$    &           & \ce{O=Mo=O}  & wag  \\
292      & $B_{3g}$     & $\delta$ & \ce{O=Mo=O}  & wag  \\
337      & $A_g,B_{1g}$ & $\delta$ & \ce{O-Mo-O} & bend  \\
380      & $B_{1g}$     & $\delta$ & \ce{O-Mo-O}  & scissor  \\
474      & $A_g$        & $\nu_{as}$ & \ce{O-Mo-O}  & stretch,bend  \\
667      & $B_{2g},B_{3g}$ & $\nu_{as}$  & \ce{O-Mo-O}  & stretch  \\
819      & $A_g$        & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
996      & $A_g$         & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
\bottomrule
\end{tabular}

@@

The growth process of the 1D \ce{MoO3} nanoflakes in non-catalytic experiment can be explained by the \gls{vs} mechanism, as proposed in other vapor phase depositions of \ce{MoO3} nanostructures.\cite{Brezesinski2010, Kalantar-zadeh2010} It has been shown that \ce{MoO3} growth on the NaOH treated Si substrates exhibited dramatic differences. Previous study in our group had found that \ce{MoO3} deposition on ITO glass exhibited new morphologies that were not observed on Si substrates under the same growth conditions, yet the mechanism was not well investigated.\cite{predeep2011} A list of composition difference between glass and Si substrate show the additional elements of Na, K, and Ca, \emph{etc} in glass. Since the concentration of Na is highest among these extra elements, it is most likely to induce the new morphology growth. Therefore, a \gls{vls} mechanism may exist for the \ce{MoO3} growth when alkali metal ions are involved. To provide a proper context, \gls{vls} process is briefly introduced here.

@@

Back to the \ce{MoO3} and alkali metal ions, a literature search found that there exists a \ce{Na2MoO4}-\ce{MoO3} phase diagram, as shown in Fig.~\ref{fig:ch4pd}.\cite{Hoermann1929} Note that the phases of the Na-Mo-O system can be written as \ce{Na2O.nMoO3}, where n = 1, 2, 3, and 4. 
%phase diagram
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{moo3_pdsmall}
\caption[Phase diagram of \ce{Na2MoO4} and \ce{MoO3}]{Phase diagram of \ce{Na2MoO4}-\ce{MoO3} reproduced from Ref.~\cite{Hoermann1929}}
\label{fig:ch4pd}
\end{figure}
Based on this phase diagram, the physical constants of reactants in Table~\ref{tb:mothermo}, and the growth conditions adopted in this study, it was predicted that the overall reactions occurred in the following sequences. First, Mo powder was oxidized, and \ce{MoO3} vapor was produced and transported to downstream by Ar carrier gas. Then, NaOH reacted with the incoming \ce{MoO3} vapor according to Formula~\ref{eq:pd}. 
\begin{subequations}\label{eq:pd}
\begin{align}
\cee{NaOH(l) + MoO3(g) &\rightarrow Na2MoO4 + H2O(g)\\
Na2MoO4 + nMoO3   &\rightarrow Na2O.(n + 1)MoO3}
\end{align}
\end{subequations}
The melting point of \ce{Na2MoO4} is 687 \si{\degreeCelsius}. Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate was located in temperature zone between 650 and 350 \si{\degreeCelsius}. The actual temperature distribution during growth was different from ambient measurement due to the pressure change and thermal conduction along the Si substrate. It was difficult to acquire the accurate temperatures along the substrate; however, by considering the flow rate, the actual temperature should be higher than that predicted by open air measurement.\cite{Subannajui2010} The continuous supply of \ce{MoO3} growth species pushed the phase evolution towards high \ce{MoO3} molar ratio end, with $n$ in \ce{Na2O.nMoO3} increasing from 1 to 4. Each site of \ce{Na2MoO4} continued absorb incoming \ce{MoO3}, forming a swelling particle. \ce{MoO3} precipitated from these seeds when a critical supersaturation concentration was reached, which was about 75\% in unit of mole according to Fig.~\ref{fig:ch4pd}. This ratio considerably exceeded that of the usual metal catalyst scenario, such as the Au-Si system. This high solubility accounted for several observations in current experiments: the dimensions of individual deposit was much larger than that of initial particle and the concentration of sodium in final products was extremely low. Based on this aforementioned analysis, the author proposed following hypothesis:

\emph{The reaction on NaOH-Si substrate follows the phase diagram, and \ce{Na2Mo4O13} serves as the catalyst promoting various 1D \ce{MoO3} growth.}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{mooe_sem_ev}
\caption[Evolution of the second stage on \ce{MoO3} growth]{Growth evolution of the second stage of catalyst-assisted growth of \ce{MoO3} 1D structures: SEM images of the deposition at different growth temperatures with growth time of row 1: 15 min, row 2: 30 min, row 3: 60 min, and row 4: 90 min.}
\label{fig:ch4ev}
\end{figure}
To reveal the growth mechanisms for the long 1D structures in the second stage, specimens were carefully examined to locate the catalyst particles. Small catalyst particles ranging from several hundred nanometers to several micrometers were found at different locations of these long 1D structures. As shown in Fig.~\ref{fig:ch4edx1} and Fig.~\ref{fig:ch4edx2}, EDX element analysis confirmed the presence of Na, Mo, and O in these particles, suggesting the particles were sodium molybdate catalysts.

@@

The first stage was dominated by transverse growth. The atomic steps in proposed growth model were depicted in the upper panel of Fig.~\ref{fig:ch4vls}. It has been verified that \ce{Na2Mo4O13} formed during the early stage of growth and acted as catalysts. Although the exact phase (liquid or solid) of \ce{Na2Mo4O13} was not known yet in current study, it can be deduced that the \ce{Na2Mo4O13} existed as an active site for the adsorption of incoming \ce{MoO3} growth species. When the catalyst was smaller than some critical size, there is no preferred growth direction. This changed when the precipitated solid exceeded certain critical dimension, and the morphology evolution was then determined by the relative size of already formed solid and the associated catalyst. Several pathways could occur after the accommodation of \ce{MoO3} vapor and supersaturation. \ce{MoO3} could precipitate at catalyst-deposition interface, or propagate along catalyst-environment boundary and spread on the already formed \ce{MoO3} surface. Meanwhile, the \gls{vs} process is not suppressed and \ce{MoO3} adatoms could directly condense on \ce{MoO3} surface.

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{vls_mode2}
\caption[Schematic drawing on the growth steps of the proposed growth mode]{Schematic drawing on the growth steps of the proposed growth mode.}
\label{fig:ch4vls}
\end{figure}

Some unique features of \ce{MoO3} must be taken into consideration to properly evaluate the dominate pathway(s). It has been reported that \ce{MoO3} can spontaneously spread over the surface of supports (\emph{e.g.} \ce{Al2O3}, \ce{SiO2}, and Au) to form a monolayer or submonolayer at a temperature (257 \si{\degreeCelsius}) well below the melting point.\cite{Leyrer1990} This strong spreading behavior can be explained by the solid-solid wetting process, in which the driving force was the decrease in total surface free energy.\cite{Leyrer1988} Although the detailed transport mechanisms of the spreading are still in debate, it is suggested that the high mobility of the Mo oxide species on substrates and \ce{MoO3} islands can promote the spreading and the ambient gases could further enhance the spreading.\cite{Gunther2000, Song2003} Based on above analysis and the final morphology of \ce{MoO3}, the dominance of accommodation and spreading pathway in higher temperature part of the growth sample was most possible in this study. Hereby the transverse growth mode was attributed to the strong spreading capability of \ce{MoO3}. The final morphology of observed nanoplate and nanobelt was a combined result of \gls{vs} and \gls{vls} growth. On the other hand, the tower-like structures in the second stage followed the axial growth mode in conventional VLS process. The molybdates can be evaporated from the higher temperature end and re-condense onto the lower temperature region. As illustrated in the lower panel of Fig.~\ref{fig:ch4vls}, this could initiate either belt growth or tower growth depending on the locations. The microtowers in this study primarily grew at the low temperature end of the substrate, where the spreading capability of the Mo oxide species was possibly limited. Thus the transverse growth pathway was probably suppressed and axial growth became dominant. The above analysis was substantiated by the multiple observation revealed by SEM imaging, as shown in Fig.~\ref{fig:ch4msch}.
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{moo3_sche}
\caption[SEM images for catalytic \ce{MoO3} growth]{SEM images for catalytic \ce{MoO3} growth: SEM images showing catalyst particles at different locations: (a) tip of a forked nanplate, (b) middle of a nanobelt, and (c) tip of another thin nanobelt; SEM images of microtowers with different morphologies: (d) cylindrical shape with tapered tip, (e) flat top, and (f) cone shape. }
\label{fig:ch4msch}
\end{figure}

>>>>

Researchers have been exploring a variety of methods to synthesize different \ce{MoO3} nanostructures. Only a brief introduction will be given here, since these efforts has been well documented in several review articles.\cite{He2003} Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor deposition approaches.\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009} Both methods have their own merits. Hydrothermal process usually needs lower temperature (\textless 300 \si{\degreeCelsius}), but the reaction often requires tens of hours, and the sample requires several post-growth processing steps; whereas vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) with a few hours reaction time. Both methods are scalable for industrial applications. However, the hydrothermal treatment seems to allow more  nanostructures control than does the vapor deposition method. Nanobelts,\cite{Li2002b} helical nanosheets, nanoflowers, nanorods,\cite{Li2006a} and nanoribbons\cite{Camacho-Bragado2006} were obtained by the former one while nanoflakes,\cite{Chen2009} nanobelts,\cite{Hu2009} and nanowires\citep{Zhou2003b,Chen2011b} dominated the product morphology for the latter one. The assistance of Au catalyst in vapor deposition only altered the orientation\cite{Yan2009} or served as preferred nucleation sites\cite{Cai2011} without producing new \ce{MoO3} structures. \citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method and demonstrated the photodegradation of methylene blue (MB) under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity, and temperature was studied. h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH-} were possible structure directing and stable agents. The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0$ eV. Hexagonal phase of \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$). It is worth noting that in spite of these numerous growth of \ce{MoO3}, reports on catalytic growth are still scarce.

@@

Silicon substrate was first cleaned according to the procedures stated in Sec.~\ref{ch2sub} on page~\pageref{ch2sub} and directly used in non-catalyst-assisted experiment. In catalyst-assisted growth, hydrophilic Si substrates were first drop-cast with \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) solution (54 $\mu$L 10 mM) and then air dried in a chemical fume hood before experiment. Other alkali ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass (Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping. Mica was cleaved right before growth without other treatment. 
\begin{table}[htb]
\centering
\caption{Physical constants of reactants }\label{tb:mothermo}
\begin{tabular}{lccr}
\toprule
Material & MP(\si{\degreeCelsius}) & BP(\si{\degreeCelsius}) & Reference\\
\midrule
\ce{NaOH}        & 318 & 1388 & \cite{crc1977}  \\
\ce{NaI}         & 651 & 1300 & \cite{crc1977}    \\
\ce{KI}          & 681 & 1330 & \cite{crc1977}   \\
\ce{Na2CO3}      & 851 & Not determined & \cite{crc1977}    \\
\ce{Na2MoO4}     & 687 & Not available & \cite{crc1977}   \\
\ce{MoO3}    & 795 & 1155 & \cite{crc1977}   \\
\ce{MoO2}    & 1100(decomp) & Not available & MSDS   \\
\bottomrule
\end{tabular}
\end{table}
In a typical catalytic synthesis (Fig.~\ref{fig:mooxgrowth}), molybdenum powders were loaded at the center of  the reaction chamber with the receiving substrate placed at the downstream. The reaction chamber was first pumped down to $\sim$10 mTorr, and then brought up to $\sim$200 mTorr with 10 sccm \ce{O2} and 10 sccm Ar.
% cvd layout
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{CVD_and_temp_MoO3.jpg}
\caption[CVD growth setup of \ce{MoO3}]{CVD growth setup of \ce{MoO3}. The triangular labels $\blacktriangledown$ were measured points at ambient environment.}
\label{fig:mooxgrowth}
\end{figure}
The heating temperature at the center was ramped up to 800 \si{\degreeCelsius} in 30 min and lasted for 120 min. Then the heating power was turned off, and the chamber was allowed to naturally cool to room temperature. During the growth, the growth temperature along the substrate was about 620 \si{\degreeCelsius} to 300 \si{\degreeCelsius} according to the temperature profile measured at atmospheric pressure. Non-catalytic growth shared the same procedure except the NaOH treatment on Si substrates.

@@

As shown in Fig.~\ref{fig:mooxch}, the crystal structure and phase of the as-synthesized specimen were examined by XRD and Raman. The XRD pattern (Fig.~\ref{fig:moxrd}) was readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628 \AA, \emph{b}=13.855 \AA, and \emph{c}=3.6964 \AA). The space group is $D_{2h}^{16}(Pbnm)$. This crystal structure is indeed a unique example among transition metal oxides, representing a transitional stage between tetrahedra and octahedral coordination.\cite{Itoh2001a} The strongest peak index was (110), suggesting the orientation of \ce{MoO3} was not parallel to the substrate, in consistent with the morphology displayed in Fig.~\ref{fig:mosem1}. In contrast, different dominating orientation was observed in the XRD pattern from catalytic growth (Sec.~\ref{sec:nasi}).
% xrd raman
% 081113 sample
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:moxrd}\includegraphics[width=0.45\textwidth]{xrd_moo3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:moram}\includegraphics[width=0.45\textwidth]{raman_moo3}}
\caption[Crystalline phase characterization of \ce{MoO3} on Si]{Crystalline phase characterization of \ce{MoO3} on Si: (a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532$ nm.}
\label{fig:mooxch}
\end{figure}
The Raman spectrum of the as-synthesized specimen also closely matched \ce{MoO3} features observed in previous studies.\cite{Dixit1986,Silveira2012} During measurement, the laser spot was carefully focused onto the \ce{MoO3} flakes, and several inspections on different positions were observed to ensure the reproductivity of spectra data. As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved. The 284 \si{cm^{-1}} peak represented the wagging mode for double bond \ce{O=Mo=O}. The 337 and 380  \si{cm^{-1}} peaks were assigned to \ce{O-Mo-O} bending and scissoring modes, respectively. The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represented \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode, and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively. The 667 \si{cm^{-1}} peak was assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral. The 819 \si{cm^{-1}} peak arose from doubly coordinated oxygen stretching mode between two octahedral. The 996 \si{cm^{-1}} peak was from unshared oxygen stretching mode.\cite{Siciliano2009} The Raman symmetry assignment is summarized in Table~\ref{tab:moram}.
% raman assign
\begin{table}[htb]
\centering
\caption[Experimental Raman peaks assignment of \ce{MoO3} on Si]{Experimental Raman peaks assignment of \ce{MoO3} on Si.\cite{Eda1992,Siciliano2009}}\label{tab:moram}
\begin{tabular}{llcll}
\toprule
this work(\si{cm^{-1}}) & Sym.  &    & Assignment &   \\
\midrule
117      & $B_{2g}$    &           & $T_c$  & RCM\textsuperscript{\emph{a}}  \\
129      & $B_{3g}$    &           & $T_c$  & RCM  \\
158      & $A_g/B_{1g}$&           & $T_b$  & RCM  \\
199      & $B_{2g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
218      & $A_g$       &           & $R_c$     & RCM  \\
247      & $B_{3g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
284      & $B_{2g}$    &           & \ce{O=Mo=O}  & wag  \\
292      & $B_{3g}$     & $\delta$ & \ce{O=Mo=O}  & wag  \\
337      & $A_g,B_{1g}$ & $\delta$ & \ce{O-Mo-O} & bend  \\
380      & $B_{1g}$     & $\delta$ & \ce{O-Mo-O}  & scissor  \\
474      & $A_g$        & $\nu_{as}$ & \ce{O-Mo-O}  & stretch,bend  \\
667      & $B_{2g},B_{3g}$ & $\nu_{as}$  & \ce{O-Mo-O}  & stretch  \\
819      & $A_g$        & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
996      & $A_g$         & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
\bottomrule
\end{tabular}

@@

The growth process of the 1D \ce{MoO3} nanoflakes in non-catalytic experiment can be explained by the \gls{vs} mechanism, as proposed in other vapor phase depositions of \ce{MoO3} nanostructures.\cite{Brezesinski2010, Kalantar-zadeh2010} It has been shown that \ce{MoO3} growth on the NaOH treated Si substrates exhibited dramatic differences. Previous study in our group had found that \ce{MoO3} deposition on ITO glass exhibited new morphologies that were not observed on Si substrates under the same growth conditions, yet the mechanism was not well investigated.\cite{predeep2011} A list of composition difference between glass and Si substrate show the additional elements of Na, K, and Ca, \emph{etc} in glass. Since the concentration of Na is highest among these extra elements, it is most likely that Na content induced the new morphology growth. Therefore, a \gls{vls} or analogous mechanism may exist for the \ce{MoO3} growth when alkali metal ions are involved. To provide a proper context, \gls{vls} process is briefly introduced here.

@@

Back to the \ce{MoO3} and alkali metal ions, a literature search found that there exists a \ce{Na2MoO4}-\ce{MoO3} phase diagram, as shown in Fig.~\ref{fig:ch4pd}.\cite{Hoermann1929} Note that the phases of the Na-Mo-O system can be written as \ce{Na2O.nMoO3}, where n = 1, 2, 3, and 4. 
%phase diagram
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{moo3_pdsmall}
\caption[Phase diagram of \ce{Na2MoO4} and \ce{MoO3}]{Phase diagram of \ce{Na2MoO4}-\ce{MoO3} reproduced from Ref.~\cite{Hoermann1929}}
\label{fig:ch4pd}
\end{figure}
Based on this phase diagram, the physical constants of reactants in Table~\ref{tb:mothermo}, and the growth conditions adopted in this study, it was predicted that the overall reactions occurred in the following sequences. First, Mo powder was oxidized, and \ce{MoO3} vapor was produced and transported to downstream by Ar carrier gas. Then, NaOH reacted with the incoming \ce{MoO3} vapor according to Formula~\ref{eq:pd}. 
\begin{subequations}\label{eq:pd}
\begin{align}
\cee{NaOH(l) + MoO3(g) &\rightarrow Na2MoO4 + H2O(g)\\
Na2MoO4 + nMoO3   &\rightarrow Na2O.(n + 1)MoO3}
\end{align}
\end{subequations}
The melting point of \ce{Na2MoO4} is 687 \si{\degreeCelsius}. Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate was located in temperature zone between 620 \si{\degreeCelsius} and 300 \si{\degreeCelsius}. Since the growth temperature range for \ce{MoO3} (525 \si{\degreeCelsius} to 300 \si{\degreeCelsius}) deposition was mainly below the lowest eutectic temperature of 507  \si{\degreeCelsius}, the majority growth of \ce{MoO3} can be explained as a \gls{vss} process, which is analogous to the VLS process except that the catalysts remain as solid particles. The actual temperature distribution during growth was different from ambient measurement due to the pressure change and thermal conduction along the Si substrate. It was difficult to acquire the accurate temperatures along the substrate; however, by considering the flow rate, the actual temperature should be higher than that predicted by open air measurement.\cite{Subannajui2010} Thus, \gls{vls} mechanism cannot be ruled out completely. The continuous supply of \ce{MoO3} growth species pushed the phase evolution towards high \ce{MoO3} molar ratio end, with $n$ in \ce{Na2O.nMoO3} increasing from 1 to 4. Each site of \ce{Na2MoO4} continued absorb incoming \ce{MoO3} growth species. \ce{MoO3} precipitated from these seeds when a critical supersaturation concentration was reached, which was about 75\% in unit of mole according to Fig.~\ref{fig:ch4pd}. This ratio considerably exceeded that of the usual metal catalyst scenario, such as the Au-Si system. This high solubility accounted for several observations in current experiments: the dimensions of individual deposit was much larger than that of initial particle and the concentration of sodium in final products was extremely low. Based on this aforementioned analysis, the author proposed following hypothesis:

\emph{The reaction on NaOH-Si substrate follows the phase diagram, and \ce{Na2Mo4O13} serves as the catalyst promoting various 1D \ce{MoO3} growth in a VSS mechanism.}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{moo3_sem_ev}
\caption[Evolution of the second stage on \ce{MoO3} growth]{Growth evolution of the second stage of catalyst-assisted growth of \ce{MoO3} 1D structures: SEM images of the deposition with growth time of (a-d) 15 min, (e-h) 30 min, (i-l) 60 min, and (m-p) 90 min at growth temperature of 525 \si{\degreeCelsius}, 445 \si{\degreeCelsius}, 390 \si{\degreeCelsius}, and 340 \si{\degreeCelsius}, respectively.}
\label{fig:ch4ev}
\end{figure}
To reveal the growth mechanisms for the long 1D structures in the second stage, specimens were carefully examined to locate the catalyst particles. Small catalyst particles ranging from several hundred nanometers to several micrometers were found at different locations of these long 1D structures. As shown in Fig.~\ref{fig:ch4edx1} and Fig.~\ref{fig:ch4edx2}, EDX element analysis confirmed the presence of Na, Mo, and O in these particles, suggesting the particles were sodium molybdate catalysts.

@@

The first stage was dominated by transverse growth. The atomic steps in proposed growth model were depicted in the upper panel of Fig.~\ref{fig:ch4vls}. It has been verified that \ce{Na2Mo4O13} formed during the early stage of growth and acted as catalysts. Although the exact phase (liquid or solid) of \ce{Na2Mo4O13} was not known yet in current study, it can be deduced that the \ce{Na2Mo4O13} existed as an active site for the adsorption of incoming \ce{MoO3} growth species. Several pathways could occur after the accommodation of \ce{MoO3} vapor and supersaturation. \ce{MoO3} could precipitate at catalyst-deposition interface, or propagate along catalyst-environment boundary and spread on the already formed \ce{MoO3} surface. Meanwhile, the \gls{vs} process is not suppressed and \ce{MoO3} adatoms could directly condense on \ce{MoO3} surface.
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{vls_mode2}
\caption[Schematic drawing on the growth steps of the proposed growth mode]{Schematic drawing on the growth steps of the proposed growth mode.}
\label{fig:ch4vls}
\end{figure}
Some unique features of \ce{MoO3} must be taken into consideration to properly evaluate the dominate pathway(s). It has been reported that \ce{MoO3} can spontaneously spread over the surface of supports (\emph{e.g.} \ce{Al2O3}, \ce{SiO2}, and Au) to form a monolayer or submonolayer at a temperature (257 \si{\degreeCelsius}) well below the melting point.\cite{Leyrer1990} This strong spreading behavior can be explained by the solid-solid wetting process, in which the driving force was the decrease in total surface free energy.\cite{Leyrer1988} Although the detailed transport mechanisms of the spreading are still in debate, it is suggested that the high mobility of the Mo oxide species on substrates and \ce{MoO3} islands can promote the spreading and the ambient gases could further enhance the spreading.\cite{Gunther2000, Song2003} Based on above analysis and the final morphology of \ce{MoO3}, the dominance of accommodation and spreading pathway in higher temperature part of the growth sample was most possible in this study. Hereby the transverse growth mode was attributed to the strong spreading capability of \ce{MoO3}. The final morphology of observed nanoplate and nanobelt was a combined result of \gls{vs} and \gls{vls} growth. On the other hand, the tower-like structures in the second stage followed the axial growth mode in conventional VLS process. The molybdates can be evaporated from the higher temperature end and re-condense onto the lower temperature region. As illustrated in the lower panel of Fig.~\ref{fig:ch4vls}, this could initiate either belt growth or tower growth depending on the locations. The microtowers in this study primarily grew at the low temperature end of the substrate, where the spreading capability of the Mo oxide species was possibly limited. Thus the transverse growth pathway was probably suppressed and axial growth became dominant. The above analysis was substantiated by the multiple observation revealed by SEM imaging, as shown in Fig.~\ref{fig:ch4msch}.
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{moo3_sche}
\caption[SEM images for catalytic \ce{MoO3} growth]{SEM images for catalytic \ce{MoO3} growth: SEM images showing catalyst particles at different locations: (a) tip of a forked nanplate, (b) middle of a nanobelt, and (c) tip of another thin nanobelt; SEM images of microtowers with different morphologies: (d) cylindrical shape with tapered tip, (e) flat top, and (f) cone shape. }
\label{fig:ch4msch}
\end{figure}
